Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-12-15 WSSSPE3/report/wg_main_best_practices.tex

Core questions that will need to be explored are in knowledge management, 
(transitions between people), reliability (reproducibility), usability, and how a software tool becomes part of the core workflow of well identified users (stakeholders)
relating to tool success and hence sustainability. \katznote{prev sentence is complex and awkward} Ideas 
that may need to be explored include:
\begin{itemize}
\item Requirements engineering to create tools with immediate uptake;
\item When should software ``die''?
\item Catering to disruptive developments in environment e.g.(new hardware, new methodology) ;
\item Dimensions of sustainability -- economic, technical, environmental, 
declining interest in primary application area), \katznote{not sure what the prev. comment goes with} social.
\end{itemize}

>>>>

Core questions that will need to be explored are in reliability (reproducibility), usability, extensibility, knowledge management and continuity (transitions between people). Answers to these will guide us on how a software tool becomes part of the core workflow of well identified users (stakeholders) relating to tool success and hence sustainability. 
\katznote{prev sentence is complex and awkward} % see fix
Ideas  that may need to be explored include:
\begin{itemize}
\item Requirements engineering to create tools with immediate uptake;
\item When should software ``die''?
\item Catering to disruptive developments in environment e.g.(new hardware, new methodology) ;
\item Dimensions of sustainability -- economic, technical, environmental and
obsolescence. 
\katznote{not sure what the prev. comment goes with} %social.
\end{itemize}
